<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{A Markdown Vignette with knitr}
-->

```{r setup, include=FALSE}
# set global chunk options
library(knitr)
opts_chunk$set(cache=FALSE)
library(knitcitations); library(reports)
bib <- read.bibtex(dir()[tools::file_ext(dir()) == "bib"][1])

BU <- "http://trinker.github.io/qdap/" 
LN <- function(fun, base=BU) paste0(BU, fun, ".html")
FUN <- function(fun, base=BU) HR2(LN(fun), paste0("<code>", fun,"</code>"))
yt <- function(url) {
  paste0("<a href=\"", url, "\" target=\"_blank\" style=\"text-decoration: none\"><b><font size=\"5\" color=\"#B22222\">[YT]</font></b></a>\n")
}
#cite in text using `r citet(bib[1])`
```
# qdap (Quantitative Discourse Analysis Package): Package Vignette
# Tyler Rinker

qdap `r citep(bib[["Rinker2013a"]])` is an R package designed to assist in quantitative discourse analysis. The package stands as a bridge between qualitative transcripts of dialogue and statistical analysis and visualization.

qdap was born out of a frustration with current discourse analysis programs. Packaged programs are a closed system, meaning the researcher using the method has little, if any, influence on the program applied to his data.

R already has thousands of excellent packages for statistics and visualization. qdap is designed to stand as a bridge between the qualitative discourse of a transcript and the computational power and freedom that R offers. As qdap returns the power to the researcher it will also allow the researcher to be more efficient and thus effective and productive in data analysis.

The qdap package is born as a means of providing researchers with the tools to analyze data and more importantly as a dynamic system governed by the data, shaped by theory and continuously refined by the field.

...if you can dream up an analysis then qdap and R can help get you there.

`r IM("https://dl.dropbox.com/u/61803503/qdap_logo.png", width=350, height=250)`

<hr>
<h3 id="toc">Select from sections below:</h3>

<div style="float: left; width: 50%;">
<ul>
<div>1.  `r HR("#project", "Starting a New Project")`    </div> 
<div>2.  `r HR("#import_export", "Import/Export Discourse Data")`  </div>  
<div>3.  `r HR("#tools", "Generic qdap Tools")`    </div> 
<div>4.  `r HR("#cleaning", "Cleaning/Preparing the Data")`    </div> 
<div>5.  `r HR("#viewing", "View the Data")`    </div> 
<div>6.  `r HR("#reshaping", "Reshaping the Data")`    </div> 
<div>7.  `r HR("#word", "Extract/Analyze Words")`    </div> 
<div>8.  `r HR("#coding", "Qualitative Coding System")`    </div> 
<div>9.  `r HR("#counts", "Word Counts and Descriptive Statistics.")`    </div> 
<div>10.  `r HR("#measures", "Word Measures and Scoring")`    </div> 
<div>11.  `r HR("#visualization", "Visualizing Discourse Data")`    </div> 
<div>12.  `r HR("#id", "ID Sentences")`    </div> 


</ul>
</div>
<div style="float: right; width: 50%;">
<ul>
<div><b>Symbol Conventions:</b></div>  
<div>`r FT(gold, 5, text="&diams;")` = Example (R code)    </div> 
<div><b>`r FT(firebrick, 5, text="[YT]")`</b> = Video Demo (click to watch)    </div> 
</ul>
</div>
<br style="clear:both;"/>


<hr>
<h3 id="project">Starting a New Project</h3>


```{r css, echo = FALSE}
options(markdown.HTML.stylesheet = "css/style.css")
```

## References
```{r, echo=FALSE, results='asis'}
#bibliography("html") 
```